Supporting Information

### 2018-04-14 SupportingInformation.Rmd
adding plot for different copula to find Moran causes

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->

>>>>

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->
```{r cause4copula, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"))}
source("Cause4copula.R")
set.seed(seed)

pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
Plotter_Cause4copula_stat(numsim=500,fcode=3,method="spearman",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/Clayton_kendall.pdf")
Plotter_Cause4copula_stat(numsim=500,fcode=3,method="spearman",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/Gumbel_spearman.pdf")
Plotter_Cause4copula_stat(numsim=500,fcode=4,method="spearman",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/Gumbel_kendall.pdf")
Plotter_Cause4copula_stat(numsim=500,fcode=4,method="kendall",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/SClayton_spearman.pdf")
Plotter_Cause4copula_stat(numsim=500,fcode=13,method="spearman",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/SClayton_kendall.pdf")
Plotter_Cause4copula_stat(numsim=500,fcode=13,method="kendall",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/SGumbel_spearman.pdf")
Plotter_Cause4copula_stat(numsim=500,fcode=14,method="spearman",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/SGumbel_kendall.pdf")
Plotter_Cause4copula_stat(numsim=500,fcode=14,method="kendall",lb=0,ub=0.1)
dev.off()
```
